\documentclass[10.5pt]{article} %Sets the default text size to 11pt and class to article.
%------------------------Dimensions--------------------------------------------
\topmargin=0.0in %length of margin at the top of the page (1 inch added by default)
\oddsidemargin=0.0in %length of margin on sides for odd pages
\evensidemargin=0in %length of margin on sides for even pages
\textwidth=6.5in %How wide you want your text to be
\marginparwidth=0.5in
\headheight=0pt %1in margins at top and bottom (1 inch is added to this value by default)
\headsep=0pt %Increase to increase white space in between headers and the top of the page
\textheight=9.0in %How tall the text body is allowed to be on each page
\pagenumbering{gobble}

\begin{document}
%These two pieces of code tell LaTeX that everything that goes in between these tags is what you want displayed as your actual document.

\centerline{{\Large \sc\bf Amit Kumar}}  %Makes whatever text you put in parenthesis move to the center
%Prevents the following text from being indented
%This is the same as a return in Latex
\centerline{\bf600 Folmar St. Apt D11\textbullet \hspace{5pt}\bf Troy, AL 36081 \textbullet \hspace{5pt} \bf (732) 589-9502}
\centerline{\bf kamit17@gmail.com}
\noindent
\line(1,0){470}\\

\noindent{\Large \bf ABOUT ME/MISSION STATEMENT}\smallskip

Iam  a driven software development professional with affinity to build engineering, release engineering and software configuration management (SCM).  To deliver software through automation, I leverage enterprise proven tooling, cutting edge software development methodologies, and automation scripting. I believe the build and release process is the heartbeat of any software development organization.  I also believe that the conversion of software code into a final marketable product represents the most important final milestone in the software development. As an SCM Build/Release architect I implement solutions that utilize well-established tools and practices - tools such as Jenkins, GIT, SVN, ClearCase,VERSATA and more. My areas of expertise include software development, scripting automation, continuous integration (CI), continuous delivery (CD), and continuous deployment (CD).

%\noindent
\medskip
\noindent
{\Large \bf PROFICIENCY}
%\smallskip
\noindent

%\noindent %Make sure that there is no line-skip for as long as you want this effect
\begin{itemize}
{\item\bf Software Development \& Scripting Languages }C , Python , Java , Bash, ANT, XML .
%\centerline{\hfill $\bullet$ C \hfill $\bullet$ Python \hfill $\bullet$ Java\hfill $\bullet$ Bash \hfill}\\
\smallskip
{\item\bf Version Control Tools: }IBM ClearCase , GIT+ GITHUB , SVN , Perforce .
%\centerline{\hfill $\bullet$ IBM ClearCase ,  Git , GitHub , SVN , Perforce }
\smallskip
%{\item \bf Application Servers / WebServer: }IBM WebSphere Application Server ,  JBoss , WAMP.
%\smallskip
%\smallskip
{\item\bf Domain Specialities :} Software Configuration Management , Continuous Delivery , Continuous Integration .
\smallskip
{\item\bf OS's  \& Platforms :} Windows (+Server 200$*$), Linux (Ubuntu, CentOS),OSX .
%{\item \bf DBMS/RDBMS:} MySQL ,  SQL
%\centerline{\hfill $\bullet$ MySQL\hfill $\bullet$ SQL\hfill}\\
\smallskip
{\item\bf SCM Infrasturcuture  :} JENKINS, IBM WebSphere Application Server , JBoss  Application Server , IBM ClearQuest , VERSATA . 
\smallskip
{\item\bf Software Methodologies/Frameworks: }Agile Methodology , ITIL , COBIT , Lean , Six Sigma.
\smallskip
\end{itemize}
\smallskip

\smallskip %This makes a large line-skip (\smallskip is also a command but has a smaller gap

\noindent{\Large \bf PROFESSIONAL EXPERIENCE} \medskip

\noindent \centerline{\large \bf Configuration Manager , CGI Technologies and Solutions\hfill Jan 2015-Present}
\begin{itemize}
  \item Managing internal and external build,packaging and release projects.
  \item Compile and assemble software using source code and store tools.
   \item Performing installations,including support  for environment issue resolution and maintenance for clients.
\end{itemize}

\smallskip

\noindent \centerline{\large \bf Graduate Assistant, Troy University \hfill Aug 2014-Dec 2014}
\begin{itemize}
  \item Performing Lab monitoring and exam proctoring duties as assigned.
  \item Assisting with the day- to - day operations of computer labs including troubleshooting, installation of hardware and software, perform additional duties as required by the supervising faculty.
\end{itemize}

\smallskip

%\noindent \centerline{\large \bf Computer Lab Assistant, Troy University \hfill Feb 2014-Aug 2014}
%\begin{itemize}
 % \item Assisting with the day- to - day operations of computer labs including troubleshooting, installation of hardware and software, perform additional duties as required by the supervising faculty.
%\end{itemize}



\noindent{\Large \bf EDUCATION}\medskip

\noindent \centerline{\large \bf Troy University \hfill 2013-2015}
\begin{itemize}
  {\item\bf M.S.Computer Science }
  \item GPA: 3.6
\end{itemize}

\noindent \centerline{\large \bf JNTU Hyderabad, India \hfill 2009-2013}
\begin{itemize}
 { \item \bf BS.Computer Science}
 % \item First Class with Distinction.
\end{itemize}

\centerline{Available for Relocation and Travel}
\end{document}